(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned: it's a Working Title.

### 2015-02-27 ms.tex
more text

EPIC 201555883 was originally listed in \paperit\ as a planet candidate.

@@

\acknowledgements
We thank [People] for [things] which improved the quality of this manuscript.

>>>>

EPIC 201555883 was originally listed in \paperit\ as a planet candidate.
After submission of that work, this object of interest was identified as 
having a transit ephemeris consistent with that of EPIC 201569483, 
which we identify as a likely eclipsing binary due to the observed transit
depth \anytodo{Right? Right?}. 
We conclude the observed transit signal from EPIC 201555883 is likely the result 
of an instrumental artifact.

Cite \citet{Coughlin14} and \citet{Batalha13} in here.

@@

\acknowledgements
We thank [Eric Agol (UW) and Other People] for [things] which improved the quality of this manuscript.
